% keefer-co-op-resume-may2014

\documentclass[10pt,letterpaper]{article}
\pagestyle{empty}

\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage{changepage}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}

\newenvironment{indentedlist}[1]%
{
\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}
}

\newcommand{\proficiency}[2]
{
\begin{tabular}{p{0.1\columnwidth} p{0.80\columnwidth}}
    \textbf{#1} & #2
\end{tabular}
}

\newcommand{\job}[4]
{
    \emph{\textbf{#1}}, #2, #3, \emph{#4}
}

\newcommand{\education}[4]
{
    \textbf{#1 (#2)}\\
    \textbf{#3}, #4
}

\begin{document}
\begin{center}
    {\Large \textbf{Keefer T. Davies}}\\		
    4A Software Engineering\\
    20382119
\end{center}
\begin{minipage}{0.33\columnwidth}
    \textbf{Local Address}\\
    250 Keats Way Unit 26\\		
    Waterloo, Ontario, Canada\\		
    N2L 6J5
\end{minipage}
\begin{minipage}{0.33\columnwidth}
    \begin{center}
	kt2davie@uwaterloo.ca\\			
	Cell: 519-636-5625
    \end{center}
\end{minipage}
\begin{minipage}{0.33\columnwidth}
    \begin{adjustwidth}{0.25\columnwidth}{}
	{\textbf{Permanent Address}}\\			
	811 Maitland Street\\			
	London, Ontario, Canada\\			
	N5Y 2W6
    \end{adjustwidth}
\end{minipage}
\vspace{1em}
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt 
\vspace{1em}
\noindent \textbf{SKILLS SUMMARY} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}    
    \begin{itemize}
	\item Dedicated team worker with an excellent work ethic and positive attitude; able to work under pressure
	\item Exceptional analytical, problem-solving and organizational skills
	\item Excellent ability to understand and follow instructions; quick learner
	\item Quick navigation and troubleshooting of operating systems and application software
    \end{itemize}
\end{adjustwidth}
\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPUTER PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{COMPUTER PROFICIENCY} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \proficiency{Languages:}{ Working knowledge of C/C$++$, Java, C\#, PHP, Python, PowerShell, JavaScript, SQL 
			     and Assembly }\\
    \proficiency{Systems:}  { Windows 7/8, OS X, Debian Linux, VMware ESX, Amazon EC2,
			      IBM MVS (Multiple Virtual Storage) Mainframe }\\
    \proficiency{Software:} { Visual Studio 2010/2013, Eclipse, Xcode, Git, Subversion, Jenkins, VersionOne, 
			      VMware vSphere, VMware Workstation, Code Collaborator, Bugzilla, WinDbg, 
			      Microsoft Office Suite, Photoshop CS4, Flash CS4, Dreamweaver CS4 }\\
    \proficiency{Other:}    { Agile Methodologies, Software Development Life Cycle (SDLC), HTML, CSS, \LaTeX, XML,
			      JSON }
\end{adjustwidth}
\vspace{0.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{WORK EXPERIENCE} \hrulefill \\[0.5em]
\job{Software Development Engineer}{McAfee Inc.}{Waterloo, ON}{January -- April 2014}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Completed several research projects in the areas of custom user interface (UI) engines, telemetry and analytics.
	\item Efficiently presented research findings in technical documents and presentations, tailored to the target audience.
	\item Resolved several production issues in McAfee's Windows applications used by millions of customers.
	\item Performed RCA (Root Cause Analysis) using WinDbg and Visual Studio to analyze software crash dumps.
    	\item Exhibited excellent interpersonal skills and demonstrated strict professional integrity.
	\item Diligently approached every task and produced a solid and creative solution often better than 
	    ideas suggested in brainstorming.
	\item Exercised the Agile methodology, participating in daily stand-up meetings, backlog grooming sessions, 
	    sprint planning meetings and PSI (Potentially Shippable Increment) planning sessions
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C/C$++$, PHP, PowerShell, Python, SQLite, WinDbg, Google Analytics and Google BigQuery 
\end{adjustwidth}
\vspace{0.5em}		
\job{Software Development Engineer}{McAfee Inc.}{Waterloo, ON}{May -- August 2013}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Managed McAfee's Jenkins Continuous Integration (CI) system, taking it from a proof of concept to a production level system with the help 
	    of one other co-op student.
	\item Created a custom Jenkins plugin that seeds build machines with the information required to perform automatic builds and 
	    deployment of McAfee products to internal test servers.
	\item Created automation tools to facilitate the automatic build process for all modules in the 
	    McAfee Total Protection suite.
	\item Implemented an automation framework with PHP and Jenkins to automate testing of the latest McAfee Stinger builds when integrated  
	    with McAfee's Windows application. This project greatly minimized manual effort and increased release frequency.  
    	\item Actively participated in design discussions for new data driven install engine.
	\item Participated in a number of community charity events including the Heart \& Stroke Big Bike event and a charity BBQ/car wash.
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C/C$++$, Java, PowerShell, Python, SQL, PHP, Jenkins and Jelly scripts
\end{adjustwidth}
\newpage
\job{Software Developer}{Research In Motion Limited}{Waterloo, ON}{September -- December 2012}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Designed, developed and maintained automation testing frameworks, tests, systems and tools for 
	    BlackBerry® Enterprise Software.
	\item Demonstrated resilience by quickly getting up to speed and making direct contributions to many different 
	    projects.
	\item Analyzed and debugged automated test suites for BlackBerry 10, identifying root causes of failure and 
	    taking appropriate corrective actions.
	\item Implemented logging functionality for test suites with Apache Log4J and AspectJ.
	\item Communicated effectively in team meetings as well as in technical discussions on internal forums.
	\item Exhibited excellent team work, integrating well with the other team members to successfully complete 
	    combined objectives.
    \end{itemize}
\end{adjustwidth}
\vspace{0.5em}
\job{IT Solutions Developer}{TD Bank Group}{London, ON}{May -- August 2011 \& January -- April 2012}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Coded, debugged and tested COBOL, JCL and SAS code on an IBM MVS Mainframe.
	\item Delivered software solutions within project schedule / timelines; showed ability to work under pressure.
	\item Developed Java applications to automate tasks performed by the team on a daily, monthly and yearly basis.
	\item Supported applications in production, including identifying the root cause of problems and identifying 
	    options to achieve a resolution in a timely and effective manner.
	\item Demonstrated strong technical aptitude and ability to learn quickly when working with unfamiliar 
	    technologies and programming languages (IBM MVS Mainframe, DB2, COBOL, JCL and SAS).
	\item Displayed excellent written and oral communication skills through technical documents and code 
	    walk-throughs.
	\item Exhibited ability to multi-task and work effectively as a team and individually.
    \end{itemize}
\end{adjustwidth}
\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{EDUCATION} \hrulefill \\[0.5em]
\education{University of Waterloo}{Waterloo, ON}{Bachelor of Software Engineering}{projected completion 2015}\\[1em]
\education{London Central Secondary School}{London, ON}{Ontario High School Diploma}{University Level, 2006-2010}\\[1em]
%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS AND SCHOLARSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{AWARDS AND SCHOLARSHIPS} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item \emph{Sandford Fleming Foundation Award}, University of Waterloo, Waterloo, ON, December 2012 
	    (for co-op work report)
	\item \emph{Merit Scholarship}, University of Waterloo, Waterloo, ON, August 2010 
	    (for high school admission average)
	\item \emph{Ontario Scholar Certificate}, London Central Secondary School, London, ON, June 2010
	\item \emph{Ontario Semifinalist}, ECOO Programming Competition, London, ON, April 2010
	\item \emph{Certificate of Excellence}, University of Toronto, Toronto, ON, April 2009 
	    (finalist in showCaSe: A Computer Science Fair 2009)
	\item \emph{Ontario Semifinalist}, ECOO Programming Competition, London, ON, April 2009
    \end{itemize}
\end{adjustwidth}
\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACTIVITIES AND INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACTIVITIES AND INTERESTS} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Enjoy playing clarinet, weight lifting, swimming, fishing, boating, downhill skiing, 
	    web design, photography, and graphic design
    \end{itemize}
\end{adjustwidth}
\begin{center}
	\textbf{\textit{References available upon request}}
\end{center}
\end{document}


