% keefer-co-op-resume

\documentclass[10pt,letterpaper]{article}
\pagestyle{empty}

\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage{changepage}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}


\newenvironment{indentedlist}[1]%
{
\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}
}

\newcommand{\proficiency}[2]
{
\begin{tabular}{p{0.1\columnwidth} p{0.80\columnwidth}}
    \textbf{#1} & #2
\end{tabular}
}

\newcommand{\job}[4]
{
    \emph{\textbf{#1}}, #2, #3, \emph{#4}
}

\newcommand{\education}[4]
{
    \textbf{#1 (#2)} \textbf{#3}, #4
}

\begin{document}
\begin{center}
    {\Large \textbf{Keefer T. Davies}}\\
    Software Engineer\\
    \vspace{1em}
    272 Activa Avenue, Kitchener, Ontario, Canada N2E 3T9\\
    \vspace{1em}
    keefer.davies@gmail.com\\
    519-636-5625
\end{center}
\vspace{1em}
\hrule width \hsize height 2pt
\vspace{1em}
\noindent \textbf{SKILLS SUMMARY} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
    \item Dedicated team worker with an excellent work ethic and positive attitude
	\item Excellent background in object oriented programming and design
	\item Strong understanding of software architecture and design patterns
	\item Experience with the Software Development Life Cycle (SDLC) and Agile Methodologies (SCRUM)
	\item Exceptional analytical, time management, communication and problem-solving skills
	\item Strong leadership skills: approachable, loyal, organized, empathetic, collaborative and adaptable
    \end{itemize}
\end{adjustwidth}
\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPUTER PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{COMPUTER PROFICIENCY} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \proficiency{Languages:}{ Proficient in C/C$++$. Working knowledge of GoLang, C\#, Java, JavaScript, Python, PowerShell and SQL. }\\
    \proficiency{Systems:}{ Windows 10, OS X, Debian Linux, Amazon Web Services (AWS), Kubernetes, Docker}\\
    \proficiency{Software:}{ Visual Studio, Xcode, Git, Subversion, Jenkins, Atlassian Suite, Databricks, Google Analytics, Intel VTune, HyperV, Code Collaborator, WinDbg }\\
    \proficiency{Other:}{ Universal Windows Platform (UWP), Google Test, Google Mock, Google Benchmark, ASP .NET Core, ReactJS, HTML, CSS, \LaTeX }
\end{adjustwidth}
\vspace{0.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{WORK EXPERIENCE} \hrulefill \\[0.5em]
\job{Lead Software Engineer}{McAfee LLC}{Waterloo, ON}{March 2019 -- current}
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}    
    \item Lead development of a brand new product with very aggressive timelines now serving over 80 million devices.
    \item Responsible for designing and building the full software stack (native UWP app, single page web application, authentication/api server).
    \item Participated in all aspects of the SDLC, from product requirement definition to product deployment. 
    \item Worked closely with all members of the development team to identify areas of expertise. 
    \item Carefully planned and delegated work to ensure that aggressive timelines could be met.
    \item Coached a team through technical problems; solicited and provided constructive criticism as required.
    \item Carefully defined interface boundaries and documented data contracts enabling concurrent development.
    \item Performed regular check-ins with members of the development team to build morale and prevent issues before they arise.
    \item Lead incremental live demonstrations of product functionality for key business partners.
    \item Worked closely with business partners and engineers to ensure the product was meeting contractual obligations and policy.
    \item Seamlessly worked with global cross-functional teams in 6 timezones (product management, customer experience design, localization, security, dev ops, architecture).
    \item Active member of the McAfee Waterloo innovation group responsible for fast prototyping of new Windows and Cloud based technologies to be used in current and future McAfee products.
    \item Designed and prototyped a framework for capturing user attribution data through custom campaigns. 
    \item Participated in weekly business syncs with product management, legal, finance, architecture and engineering to review business contracts and discuss technical feasibility.
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C$++$, C\#, JavaScript, Python, ASP .NET Core, ReactJS 
\end{adjustwidth}
\newpage

\job{Software Engineer}{McAfee LLC}{Waterloo, ON}{July 2015 -- March 2019}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
    \item Developed, maintained, reviewed and tested high-quality modern C++ code for McAfee's Windows flagship product (McAfee Live Safe).
    \item Designed and developed a robust, plug-and-play message bus and module hosting framework to re-architect McAfee's core Windows products.
    \item Developed a modern user interface (UI) framework that enabled a revolutionary HTML5 based user interface for McAfee's flagship product. The framework is based on the Chromium Embedded Framework and connects seamlessly with the message bus.
    \item Maintained and supported a proprietary analytics stack developed to provide comprehensive real user data reporting for the McAfee True Key product. Gaining exposure to GoLang, Kubernetes, Docker and Amazon Web Services.
    \item Developed a discoverability and communication protocol that enables secure communication between UWP applications and Win32 desktop applications. \emph{US Patent No. 10657246}
    \item Designed and implemented the underlying framework for McAfee Consumer’s first persona-based suite of products (McAfee Gamer Security). 
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C/C$++$, C\#, GoLang, JavaScript, PowerShell, Python, UWP, VTune, AWS, Kubernetes
\end{adjustwidth}
\vspace{0.8em}
\job{FileMaker Software Engineer}{Apple Inc.}{Ottawa, ON}{September -- December  2014}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
    \item Resolved production issues in FileMaker Pro 13, a top selling easy-to-use database software.
    \item Practiced cross-platform development, addressing numerous bugs on Windows and OS X. Efforts were focused on addressing bugs in Script Workspace, the flagship feature in FileMaker Pro 14 (2015 release).
    \item Re-engineered a custom text wrapping algorithm for the new Script Workspace developed with the Windows Presentation Foundation (WPF).
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C/C$++$, WPF/C\#, Cocoa/Objective-C, FileMaker Pro Advanced
\end{adjustwidth}
\vspace{0.8em}
\job{Software Development Engineer}{McAfee Inc.}{Waterloo, ON}{ May -- August 2013 \& January -- April 2014 }\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
	\item Completed several research projects in the areas of custom UI engines, telemetry and analytics.
	\item Managed McAfee's Jenkins Continuous Integration (CI) system, taking it from a proof of concept to a production level system.
    \end{itemize}
    \vspace{0.5em}
    \textbf{Technologies:} C/C$++$, C\#, Java, PowerShell, Python, PHP, SQL, SQLite, WinDbg, Jenkins and Jelly scripts
\end{adjustwidth}
\vspace{0.8em}
\job{Software Developer}{Research In Motion Limited}{Waterloo, ON}{September -- December 2012}\\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
        \item Designed, developed and maintained automation testing frameworks, tests, systems and tools for BlackBerry® Enterprise Software.
        \item Analyzed and debugged automated test suites for BlackBerry 10, identifying root causes of failure and took appropriate corrective actions.
        \item Implemented logging functionality for test suites with Apache Log4J and AspectJ.
    \end{itemize}
    \vspace{0.5em}    
    \textbf{Technologies:} C/C$++$, C\#, Java, Python, Jenkins, Gerrit, QNX Momentics IDE, and Spring Tool Suite
\end{adjustwidth}
\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{EDUCATION} \hrulefill \\[0.5em]
\education{University of Waterloo}{Waterloo, ON}{Bachelor of Software Engineering}{2010-2015}\\[1em]
\education{London Central Secondary School}{London, ON}{Ontario High School Diploma}{University Level, 2006-2010}\\[1em]
%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS AND SCHOLARSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{AWARDS, SCHOLARSHIPS AND PATENTS} \hrulefill \\
\begin{adjustwidth}{0.1in}{0.5in}
    \begin{itemize}
    \item \emph{Authenticated Discoverability of Universal Windows Applications to WIN32 Desktop Applications}, McAfee LLC, Waterloo, ON, May 2020
	    (US Patent No. 10657246)
	\item \emph{Sandford Fleming Foundation Award}, University of Waterloo, Waterloo, ON, December 2012
	    (best technical writing)
	\item \emph{Merit Scholarship}, University of Waterloo, Waterloo, ON, August 2010
	    (admission average)
    \end{itemize}
\end{adjustwidth}
\vspace{1em}
\begin{center}
	\textbf{\textit{References available upon request}}
\end{center}
\end{document}


